### 2015-12-09 AssignmentVIII/Assignment8-Ditz_Schroeder-WS15-16.tex
aufgabe 2 b ist fertig

\subsection*{a}
Assume a text $T$ of length $n$ with $n$ times the letter ``a''. If one build a suffix tree for $T$ 
using WOTD, each node will have just one c-group with all remaining suffixes in it. So evaluating the 
root node, one has to compute the longest common prefix of $n$ suffixes, of $n-1$ suffixes for the 
second node and so on. In each c-group the shortest suffix is of length $1$, so for each node $\bar{u}$ 
there are just $|R_a{\bar{u}}|$ numbers of comparisons.

@@

\subsection*{b}

>>>>

\subsection*{a}
Assume a text $T$ of length $n$ with $n$ times the letter ``a''. If one build a suffix tree for $T$ 
using WOTD, each node will have just one c-group with all remaining suffixes in it. So evaluating the 
root node, one has to compute the longest common prefix of $n$ suffixes, of $n-1$ suffixes for the 
second node and so on. In each c-group the shortest suffix is of length $1$, so for each node $\overline{u}$ 
there are just $|R_a\{\overline{u}\}|$ numbers of comparisons.

@@

\subsection*{b}
Suffix links are defined as an auxiliary edge that point from branching node $\overline{bw}$ to the branching 
node $\overline{w}$, if it exists and to the root otherwise. If we now defined a suffix link, such that it 
points into the other direction (i.e. from branching node $\overline{w}$ to branching node $\overline{bw}$) gives 
us an efficient method to find maximal unique matches. If we now find a branching node that indicates 
a unique match (for definition see script) and there is a suffix link that point to another branching node, we know that the current 
branching node is not a maximal unique match (because it is not left maximal). So we just have to 
follow the suffix links until we reach a branching node without an outgoing suffix link and we have 
found a maximal unique match.
